Constraining Quiescent Supermassive Black Hole Environments.

### 2014-08-11 ms.tex
Some changes to table, some minor improvements to language

The accretion rate is proportional to the stellar mass enclosed inside of $\rs$, so for core galaxies $\dot{M}\sim \Mbh (\rs/\rsoi)^{2}$, while for cusp galaxies $dot{M}\sim \Mbh (\rs/\rsoi)$.  This steeper dependence is enough to offset the tendency for core galaxies to have a larger $\rs/\rsoi$ for fixed $\eta$ (see Figure~\ref{fig:stag})Therefore, for $\rs/\rsoi<1$ core galaxies would have a smaller $\dot{M}$ than cusp galaxies.  For $\vwO=1000$ km/s, core galaxies have a smaller accretion rate for a given black hole mass.

@@

For $\vwO$=1000 km/s, it is apparent from Figure~\ref{fig:cooling}, that radiative cooling may be safely neglected. With a few exceptions this is also true for $\vwO$=500 km/s.  However, for $\vwO$=200 km/s cooling may be quite important. For smaller $\eta$ the effects of cooling will be less pronounced. For each of our galaxies we give the maximum $\eta$ such that $H/C >$1 in Table .  Roughly speaking, this is the maximum $\eta$ for which it would be safe to ignore cooling. $\eta$ depends on the age of the stellar population, and will realistically vary between $\sim 0.1$ and $\sim 1$.

>>>>

The accretion rate is proportional to the stellar mass enclosed inside of $\rs$, so for core galaxies $\dot{M}\sim \Mbh (\rs/\rsoi)^{2}$, while for cusp galaxies $\dot{M}\sim \Mbh (\rs/\rsoi)$.  This steeper dependence is enough to offset the tendency for core galaxies to have a larger $\rs/\rsoi$ for fixed $\eta$ (see Figure~\ref{fig:stag}). Therefore, for $\rs/\rsoi<1$ core galaxies would have a smaller $\dot{M}$ than cusp galaxies.  For $\vwO=1000$ km/s, core galaxies have a smaller accretion rate for a given black hole mass.

@@

For $\vwO$=1000 km/s, it is apparent from Figure~\ref{fig:cooling}, that radiative cooling may be safely neglected. With a few exceptions this is also true for $\vwO$=500 km/s.  However, for $\vwO$=200 km/s cooling may be quite important.

For small $\eta$ the effects of cooling will be less pronounced. For each of our galaxies we give the maximum $\eta$ such that $H/C >$1 in Table .  Roughly speaking, this is the maximum $\eta$ for which it would be safe to ignore cooling. $\eta$ depends on the age of the stellar population, and will realistically vary between $\sim 0.1$ and $\sim 1$.
